---
title: "LIWC Analysis"
output: html_document
---
```{r}
library(tidyverse)
library(readxl)
library(magrittr)
library(tidytext)
library(topicmodels)
library(tm)
```
```{r}
d.0 <- read_csv("../data/final_raw/JTBD CSV Transcript v2.csv")
```

```{r}
names(d.0)
```
```{r}
f_ = "../data/final_raw/JTBD CSV Transcript v2.csv"
text_column = grep('ALL QUOTES', names(d.0))
id_column = grep('PARTICIPANT ID', names(d.0))

(cmd_ = paste0(
  'liwc-22-cli -m wc ',
  '--input ', shQuote(f_), ' ',
  '--output ', '../results/liwc_output/liwc_default_dictionary_scores.csv ',
  '--row-id-indices ', id_column, ' ',
  '--column-indices ', text_column
))
# Run these through LIWC using the CLI
system(cmd_)
```
# Process results

1. The Summary scores are in rows `Analytic` through `Tone` with normed scores

2. Other LIWC dictionary scores of interest (from TT docs) are in % of text format

```{r}
res.0 = read_csv("../results/liwc_output/liwc_default_dictionary_scores.csv") %>%
  # Rename the Participant ID column to match the original data
  select(`PARTICIPANT ID` = `Row ID`, everything())
summary_df = res.0 %>%
  select(`PARTICIPANT ID`, Analytic:Tone)
scores_df = res.0 %>%
  select(
    `PARTICIPANT ID`,
    Drives, affiliation, achieve, power,
    Cognition, allnone:memory,
    Affect, tone_pos:emo_sad,
    # Others
    focuspast,focuspresent,focusfuture,
    leisure, work, money, wellness, tech, need, want, lack, visual, auditory, feeling
  )
```

# Now use a custom dictionaries

1. Personal Values Dictionary

2. Brand personality

```{r}
pv_cmd_ = paste0(cmd_, ' ' , '--dictionary ../dictionaries/personal-values-dictionary.dicx')
pv_cmd_ %<>% 
  str_replace('--output.+_scores.csv', '--output ../results/liwc_output/personal-values_results.csv')
bp_cmd_ = paste0(cmd_, ' ' , '--dictionary ../dictionaries/brand-personality-dictionary.dicx')
bp_cmd_ %<>% 
  str_replace('--output.+_scores.csv', '--output ../results/liwc_output/brand-personality_results.csv')
pv_cmd_
bp_cmd_
```
```{r}
system(pv_cmd_)
system(bp_cmd_)
```

```{r}
pv_res = read_csv("../results/liwc_output/personal-values_results.csv") %>%
  select(`PARTICIPANT ID` = `Row ID`, Dic:last_col()) %>%
  select(-Dic, -AllPunc:-last_col())
bp_res = read_csv("../results/liwc_output/brand-personality_results.csv") %>%
  select(`PARTICIPANT ID` = `Row ID`, Dic:last_col())  %>%
  select(-Dic, -AllPunc:-last_col())
pv_res %>% head
bp_res %>% head
```

# Merge all scores into master data frame
```{r}
df = reduce(
  list(d.0 %>% select(`PARTICIPANT ID`, Segment), 
       summary_df %>% rename_with(.fn = ~paste0('normed_', .), .cols = -1), 
       scores_df,
       pv_res %>% rename_with(.fn = ~paste0('pv_', .), .cols = -1),
       bp_res %>% rename_with(.fn = ~paste0('bp_', .), .cols = -1)
  ),
  left_join
) %>%
  mutate(across(Segment, factor))

levels(df$Segment)

write.csv(df, "../results/LIWC-master_raw.csv", row.names = F)
```

# For each feature, run an anova using segment
```{r}
fit_anova = function(X) {
  return(list(lm(X ~ df$Segment)))
}

get_f_stat = function(lm_) {
  summary(lm_)$fstatistic[1]
}

get_f_pvalue = function(lm_) {
  fstat <- summary(lm_)$fstatistic
  pf(fstat[1], fstat[2], fstat[3], lower.tail = F)
}

get_signif = function(p_) {
  p_ < .05
}

# The next one will be unnest wider afterward
get_group_descriptives = function(lm_, group_) {
  mod_mat <- lm_$model
  list(
    M = mean(mod_mat[mod_mat[,2] == group_, 1]),
    SE = sd(mod_mat[mod_mat[,2] == group_, 1]) / sqrt(sum(mod_mat[,2] == group_))
  )
}

analysis_res = df %>%
  select(-`PARTICIPANT ID`, -Segment) %>%
  pivot_longer(everything(), names_to = 'variable', values_to = 'data_') %>%
  summarise(across(data_, fit_anova), .by = variable) %>%
  rowwise() %>%
  mutate(
    f = get_f_stat(data_),
    p = get_f_pvalue(data_),
    adjusted_p_bonf = p.adjust(p, 'bonf', ncol(df) - 2), # create placeholder
    adjusted_p_signif = p < .05, # Also placeholder
    Consumer = list(get_group_descriptives(data_, 'Consumer')),
    PC = list(get_group_descriptives(data_, 'PC')),
    Server = list(get_group_descriptives(data_, 'Server')),
    Storage = list(get_group_descriptives(data_, 'Storage'))
  ) %>%
  unnest_wider(col = c(Consumer, PC, Server, Storage),
               names_sep = '_') %>%
  mutate(across(adjusted_p_bonf, ~p.adjust(p, 'bonf', ncol(df) - 2)),
         across(adjusted_p_signif, ~(adjusted_p_bonf < .05))) %>%
  arrange(desc(abs(f)))
```   
```{r}
write.csv(analysis_res %>% select(-data_), "../results/unfiltered_segment-ANOVA.csv", row.names = F)
```


# Plot
```{r}
plt.dat = analysis_res %>%
    #filter(p < .05) # For unadjusted
    filter(adjusted_p_signif) %>% # could also use above
    mutate(across(variable, ~factor(., levels = .))) %>%
    select(variable, contains('_M'), contains('_SE')) %>%
    pivot_longer(-variable, names_to = 'stat', values_to = 'estimate') %>%
    mutate(Segment = factor(str_replace(stat, '_.+$', ''), 
                            levels = rev(c("Consumer", "PC", "Server", "Storage"))),
           across(stat, ~str_replace(., '^.+_', ''))) %>%
    pivot_wider(id_cols = c(Segment, variable), names_from = stat, values_from = estimate) %>%
    mutate(conf_upr = M + 1.96*SE, conf_lwr = M - 1.96*SE)

plt.dat %>%
  ggplot(aes(x = M)) +
  geom_col(aes(y = Segment, fill = Segment)) +
  geom_errorbar(aes(y = Segment, xmax = conf_upr, xmin = conf_lwr),
                width = .15) +
  facet_wrap(~variable, scales = 'free_x') +
  theme_bw(base_size = 14) +
  ylab('') +
  xlab('Mean LIWC Score') +
  ggtitle(label = 'LIWC Features that significantlyª distinguished segment groups',
          subtitle = 'ªSignificance determined after adjusting p-values') +
  theme(plot.title.position = 'plot',
        plot.title = element_text(hjust = .5),
        plot.subtitle = element_text(hjust = .5)) +
  guides(fill = guide_legend(reverse = T))
  
ggsave("../plots/LIWC-Scores_ANOVA-facet-barplot.jpg",
       units = 'in', device = 'jpg', height = 9, width = 13.5)
```
```{r}
analysis_res %>%
    filter(p < .05) %>% # For unadjusted
    #filter(adjusted_p_signif) %>% # could also use above
  mutate(across(variable, ~factor(., levels = .))) %>%
    select(variable, contains('_M'), contains('_SE')) %>%
    pivot_longer(-variable, names_to = 'stat', values_to = 'estimate') %>%
    mutate(Segment = factor(str_replace(stat, '_.+$', ''), 
                            levels = rev(c("Consumer", "PC", "Server", "Storage"))),
           across(stat, ~str_replace(., '^.+_', ''))) %>%
    pivot_wider(id_cols = c(Segment, variable), names_from = stat, values_from = estimate) %>%
    mutate(conf_upr = M + 1.96*SE, conf_lwr = M - 1.96*SE) %>%

#plt.dat %>%
  ggplot(aes(x = M)) +
  geom_col(aes(y = Segment, fill = Segment)) +
  geom_errorbar(aes(y = Segment, xmax = conf_upr, xmin = conf_lwr),
                width = .15) +
  facet_wrap(~variable, scales = 'free_x') +
  theme_bw(base_size = 14) +
  ylab('') +
  xlab('Mean LIWC Score') +
  ggtitle(label = 'LIWC Features that significantly distinguished segment groups') +
  theme(plot.title.position = 'plot',
        plot.title = element_text(hjust = .5),
        plot.subtitle = element_text(hjust = .5)) +
  guides(fill = guide_legend(reverse = T))
  
ggsave("../plots/UNADJUSTED-P_LIWC-Scores_ANOVA-facet-barplot.jpg",
       units = 'in', device = 'jpg', height = 9, width = 13.5)
```


# One plot for each feature
```{r}
analysis_res %>%
  filter(p < .05) %>%
  mutate(across(variable, ~factor(., levels = .))) %>%
  select(variable, contains('_M'), contains('_SE')) %>%
  pivot_longer(-variable, names_to = 'stat', values_to = 'estimate') %>%
  mutate(Segment = factor(str_replace(stat, '_.+$', ''), 
                          levels = rev(c("Consumer", "PC", "Server", "Storage"))),
         across(stat, ~str_replace(., '^.+_', ''))) %>%
  pivot_wider(id_cols = c(Segment, variable), names_from = stat, values_from = estimate) %>%
  mutate(conf_upr = M + 1.96*SE, conf_lwr = M - 1.96*SE) %>%
  {
    tmp <- .
    variables = unique(tmp$variable)
    walk(variables, \(v_) {
      plt_dat_ = tmp %>%
        select(Segment, M, starts_with('conf'), variable) %>%
        filter(variable == v_)
      ggplot(data = plt_dat_, aes(x = M)) +
        geom_col(aes(y = Segment, fill = Segment)) +
        geom_errorbar(aes(y = Segment, xmax = conf_upr, xmin = conf_lwr),
                      width = .15) +
        facet_wrap(~variable, scales = 'free_x') +
        theme_bw(base_size = 14) +
        ylab('') +
        xlab('Mean LIWC Score') +
        ggtitle(label = paste0('Group means for LIWC feature: ', v_)) +
        theme(plot.title.position = 'plot',
              plot.title = element_text(hjust = .5),
              plot.subtitle = element_text(hjust = .5)) +
        guides(fill = guide_legend(reverse = T))
      ggsave(paste0("../plots/significant_features/", v_, '.jpg'),
             units = 'in', device = 'jpg', height = 9 * .6667, width = 13.5 * .6667)
    })
    
  }

```




# Contextualizing trust

Taking the words surrounding trust, plot the top 5 most common words around it 
for each group and overall.
```{r}
trust = read_csv("../data/liwc_raw/LIWC-22 Results - JTBD CSV Transcript v2 - Contextualizer.csv")
segment_spine = d.0 %>%
  select(`PARTICIPANT ID`, Segment) %>%
  mutate(`Row ID` = row_number())
trust_source_grouped = left_join(trust, segment_spine) %>%
  summarise(across(`Context Left`, ~paste(., collapse = ' ')),
            across(`Context Right`, ~paste(., collapse = ' ')),
            .by = Segment) %>%
  rowwise() %>%
  mutate(context = paste(`Context Left`, `Context Right`, collapse = ' ')) %>%
  select(Segment, context)
trust_source_overall = left_join(trust, segment_spine) %>%
  summarise(across(`Context Left`, ~paste(., collapse = ' ')),
            across(`Context Right`, ~paste(., collapse = ' '))) %>%
  rowwise() %>%
  mutate(context = paste(`Context Left`, `Context Right`, collapse = ' ')) %>%
  select(context)

trust_dtm_grouped = DocumentTermMatrix(Corpus(VectorSource(trust_source_grouped$context)))
trust_dtm_overall = DocumentTermMatrix(Corpus(VectorSource(trust_source_overall$context)))

# trust counts per group
(trust_counts = trust %>% 
  summarise(trust_count = max(Observation),
            .by = `Row ID`) %>%
  left_join(segment_spine) %>%
  summarise(trust_count = sum(trust_count), num_different_speakers = n(), .by = Segment))
write.csv(trust_counts, "../results/trust-counts_grouped.csv", row.names = F)
```

```{r}
data(stop_words)
# Get top 10 words and plot frequencies
imap(trust_source_grouped$Segment, function(g, i) {
  dtm_ = as.matrix(trust_dtm_grouped)
  terms_ = colnames(dtm_)
  term_df_ = tibble(
    group = g,
    term = terms_,
    count = as.vector(dtm_[i, ])
  ) %>%
    # Remove stop words
    filter(!term %in% stop_words$word) %>%
    arrange(desc(count)) %>%
    slice(1:10) %>%
    mutate(across(term, ~factor(., levels = rev(.))))
  ggplot(term_df_) +
    geom_col(aes(y = term, x = count, fill = term), show.legend = F) +
    facet_grid(~group) +
    #guides(fill = guide_legend(reverse = T)) +
    theme_bw(base_size = 14) +
    ylab('Word') +
    xlab(paste0('Count across all participants in segment ', g)) +
    ggtitle(label = paste0('Words most commonly associated with `trust` in segment ', g)) +
    theme(plot.title.position = 'plot',
          plot.title = element_text(hjust = .5),
          plot.subtitle = element_text(hjust = .5)) +
    guides(fill = guide_legend(reverse = T)) +
  scale_x_continuous(breaks = 0:max(term_df_$count))
  ggsave(paste0("../plots/trust/", g, '.jpg'),
             units = 'in', device = 'jpg', height = 9 * .6667, width = 13.5 * .6667)
})
```

overall trust
```{r}
overall_trust_plot_data = trust_dtm_overall %>% 
  {
    tmp <- .
    dtm_ = as.matrix(tmp)
    terms_ = colnames(dtm_)
    tibble(
      term = terms_,
      count = as.vector(dtm_[1, ])
    ) %>%
      # Remove stop words
      filter(!term %in% stop_words$word) %>%
      arrange(desc(count)) %>%
      slice(1:10) %>%
      mutate(across(term, ~factor(., levels = rev(.))))
  }
  
overall_trust_plot = ggplot(overall_trust_plot_data) +
  geom_col(aes(y = term, x = count, fill = term), show.legend = F) +
  #guides(fill = guide_legend(reverse = T)) +
  theme_bw(base_size = 14) +
  ylab('Word') +
  xlab('Count') +
  ggtitle(label = 'Words most commonly associated with `trust` in the study') +
  theme(plot.title.position = 'plot',
        plot.title = element_text(hjust = .5),
        plot.subtitle = element_text(hjust = .5)) +
  guides(fill = guide_legend(reverse = T)) +
  scale_x_continuous(breaks = 0:max(overall_trust_plot_data$count))
ggsave("../plots/trust/overall_trust-context.jpg", plot = overall_trust_plot,
       units = 'in', device = 'jpg', height = 9 * .6667, width = 13.5 * .6667)
```

# LDA searching for themes
Components in the data
```{r}
library(topicmodels)
library(tm)
library(tidytext)
data("stop_words")
#library(udpipe)
# Read in raw counts and convert back to corpus
df.raw = read_csv("../data/liwc_raw/LIWC-22 Results - jtbd_csv_transcript_v1_uk_aus - MEM Raw.csv") %>%
  select(-`ALL QUOTES`:-RawTokenCount) %>%
  # drop stop words
  select(-any_of(stop_words$word))
head(df.raw)
```
```{r}
# The above is coercible to simple_triplet_matrix in same format as document-term matrices
lda.models = lapply(as.character(2:6), \(x) {
  LDA(df.raw, k = as.numeric(x))
})
# # Convert so it works wth
# doc_term_freq = df.raw %>%
#   mutate(doc_id = row_number()) %>%
#   pivot_longer(-doc_id, names_to = 'term', values_to = 'freq')
# 
# dtm = udpipe::document_term_matrix(doc_term_freq)
# view(df.raw)
```
```{r}
library(ggplot2)
library(dplyr)

plot_topics = function(lda_model) {
  top_terms = tidy(lda_model) %>%
    group_by(topic) %>%
    slice_max(beta, n = 10) %>%
    ungroup() %>%
    arrange(topic, -beta)
  
  nt = n_distinct(top_terms$topic)
  
  top_terms %>%
    mutate(term = reorder_within(term, beta, topic)) %>%
    mutate(across(topic,~paste0('Theme ', .))) %>%
    ggplot(aes(beta, term, fill = factor(topic))) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~topic, scales = "free") +
    scale_y_reordered() +
    theme_bw(base_size = 14) +
    xlab('Relative importance of word to the theme') +
    ylab('Word') +
    ggtitle(label = 'Most salient topics across all participants') +
    theme(plot.title.position = 'plot',
          plot.title = element_text(hjust = .5),
          plot.subtitle = element_text(hjust = .5)) +
    guides(fill = guide_legend(reverse = T)) +
    theme(axis.ticks.x = element_blank(),
          axis.text.x = element_blank())
  ggsave(paste0("../plots/themes/", nt, '.jpg'),
             units = 'in', device = 'jpg', height = 9 * .6667, width = 13.5 * .6667)
}

map(lda.models, plot_topics)
```

